---
title: "Using the helper functions"
author: "Michael Koohafkan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Helper Functions}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

The `arcpy` package provides a small number of helper functions to make
working with spatial layer geometries and attributes easier. These 
helper functions are essentially wrappers for the arpcy Data Access module
that support simple transfer of information between spatial layers and R
data frames.

To demonstrate the helper functions, we'll set up a workspace with a copy
of the California County Boundaries shapefile (available on https://data.ca.gov).
A copy of this file is included with the `arcpy` package.


```{r}
library(arcpy)
use_ArcGIS(pro = TRUE)

# set workspace
arcpy$env$workspace = tempdir()
arcpy$env$scratchWorkspace = tempdir()

# copy feature for example
fc = arcpy$management$CopyFeatures(system.file("CA_Counties",
  "CA_Counties_TIGER2016.shp", package = "arcpy"), "CA_Counties")
```


Reading attribute tables is accomplished using the function `da_read`.

```{r}
head(da_read(fc, fields = c("FID", "NAME")))
```

Tokens are also supported by `arcpy`. If you have the `tibble` package installed, 
you can read geometry tokens as list columns.

```{r}
da_read(fc, fields = c("OID@", "NAME", "SHAPE@TRUECENTROID"))
```

You can use `da_update` to modify attributes.

```{r}
d = da_read(fc, fields = "NAME")
d["NAME"] = paste(d$NAME, "County, CA")
da_update(fc, d)

head(da_read(fc, fields = "NAME"))
```

You can also use `da_update` to add additional fields to a table, provided 
you create the field first.

```{r, results = "hide"}
d = da_read(fc, c("ALAND", "AWATER"))
d["FRACLAND"] = d$ALAND / (d$ALAND + d$AWATER)

arcpy$management$AddField(fc, "FRACLAND", "FLOAT")
da_update(fc, d["FRACLAND"])
```

You can use `da_drop` and `da_insert` to remove and add rows, respectively.

```{r}
d = da_read(fc)
# extract second row
new.d = d[2,]
# drop second row
da_drop(fc, 2)
# add the row back
da_insert(fc, new.d)

head(da_read(fc))
```

```{r, echo = FALSE, include = FALSE}
arcpy$management$Delete(fc)
```
