---
title: "Quickstart to arcpy"
author: "Michael Koohafkan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
```

Getting started with `arcpy` in R is easy. Use the `use_ArcGIS()` 
function to connect to an ArcGIS installation. If you don't specify
a path, `arcpy` will search in the standard installation folders.
ArcGIS Desktop provides a stand-alone python installation while
ArcGIS Pro provides support for Conda virtual environments.

```{r eval = FALSE}
library(arcpy)
```

The `arcpy` package can look for ArcGIS installations in their
default locations. 

```{r}
# Search for the default ArcGIS Pro Conda Python 3.x environment
find_ArcGIS(pro = TRUE)

# use the default ArcGIS Pro Conda Python 3.x environment
use_ArcGIS(pro = TRUE)
```

The `arcpy` package automatically provides a `reticulate` module object 
called `arcpy`. This object provides the interface to ArcGIS.

```{r}
arcpy
arcpy$GetInstallInfo()$ProductName
```

Once you are connected to your ArcGIS installation, using `arcpy` functions
and classes is as seamless as using any other Python module via `reticulate`.
The `arcpy` pacakge also re-exports reticulate's `py_help` function so that 
you can access the `arcpy` documentation.


```{r}
# get and set the arcpy environment
arcpy$env$workspace = tempdir()
arcpy$env$workspace

# get help on arcpy functions
py_help(arcpy$Exists)
```

Happy scripting!
