---
title: "Quickstart to arcpy"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
```

Getting started with `arcpy` in R is easy. If you're using ArcGIS Pro,
you'll first need to create a Conda environment that will link to your
ArcGIS Pro install. For example, here's how you would create a Conda
environment to link to an ArcGIS Pro 3.1 install.

```{r eval = FALSE}
library(arcpy)

install_arcpy(version = "3.1")
```

If you don't specify the python version, the package will use the
latest compatible Python version based on what is reported in the
arcpy module build.

The `arcpy` package automatically provides a `reticulate` module object 
called `arcpy`. This object provides the interface to ArcGIS.

```{r}
arcpy
arcpy$GetInstallInfo()$ProductName
```

Once you are connected to your ArcGIS installation, using `arcpy` functions
and classes is as seamless as using any other Python module via `reticulate`.
The `arcpy` pacakge also re-exports reticulate's `py_help` function so that 
you can access the `arcpy` documentation.


```{r eval = FALSE}
# get and set the arcpy environment
arcpy$env$workspace = tempdir()
arcpy$env$workspace

# get help on arcpy functions
py_help(arcpy$Exists)
```

```{r echo = FALSE}
# get and set the arcpy environment
arcpy$env$workspace = tempdir()
arcpy$env$workspace
```


Happy scripting!
